### 2015-02-01 model.tex
System model section of paper

\documentclass[twocolumn,10pt]{article}
\usepackage{amsmath}

\begin{document}

\subsection{System model}
This work models the assignment of individual vehicles to cell towers with an effective received signal strength (eRSS) based decision process.  This eRSS between a vehicle $v$ and a cell tower $t$ is calculated from the received power by introducing tower handoff dynamics as noise penalties;
each vehicle gets assigned to the cell tower with the highest eRSS value at each time point in the simulation.
All towers are assumed to output with the same transmit power, so eRSS can be calculated in dB as: \begin{eqnarray}
  eRSS_{v-t} & = & \left( \frac{P_{RX_v}}{P_{TX_t}} \right)_{dB} 
                   + P_{handoff_{v-t}} \\
  & = & P_{d_{v-t}} +P_{int} + P_{hyst_{v-t}} + P_{load_t}.
\end{eqnarray}

In this equation, the actual received signal strength is composed of two parts, $P_d$ and $P_{int}$.  The attenuation due to path loss is given by: \begin{equation}
  P_{d_{v-t}} = -10 \gamma \log_{10} d_{v-t},
\end{equation}
where $d_{v-t}$ is the distance between the vehicle and the cell tower, and $\gamma$ is the path loss exponent.  The additional attenuation due to interference, multipath effects, and other RF noise is wrapped up into a uniformly distributed random penalty: \begin{equation}
  P_{int} = -\alpha \cdot \mathrm{Unif}(0,1).
\end{equation}

The dynamics of the tower handoff, $P_{handoff}$, are modelled using two parameters.  $P_{hyst}$ represents an amount of hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers: \begin{equation}
  P_{hyst_{v-t}} = \begin{cases}
    \beta & \mathrm{if~} v \mathrm{~is~already~connected~to~} t, \\
    0 & \mathrm{otherwise.}
  \end{cases}
\end{equation}
$P_{load}$ represents the load balancing efforts to distribute usage across the cell network, adding an eRSS penalty to heavily loaded towers: \begin{equation}
  P_{load_t} = -\xi \cdot N_{t},
\end{equation}
where $N_t$ is the number of other vehicles already connected to tower $t$.  The four parameters $\{\gamma, \alpha, \beta, \xi\}$ can be scaled by the first to get our final parameter vector $\phi = \{a, b, c\} = \{\alpha/\gamma, \beta/\gamma, \xi/\gamma\}$ over which we conduct our sensitivity analysis, evaluating the relative impacts of hysteresis and load balancing in the presence of RF noise on route flow estimation.

\subsection{Limitations}

In this work, we only consider hard handoffs, wherein each vehicle is connected to exactly one cell tower at all times.  The load balancing is represented by a linear penalty on tower utilization, which ignores nonlinear effects such as maximum tower capacity.  The units are arbitrarily scaled, and so require manual tuning to determine appropriate relative weights.

\end{document}

### 2015-02-01 main.py
full test + results!

@@ -185,15 +185,15 @@ def experiment(m=2,fname=None):
     # spreadlist = (np.logspace(0,1,10, base=3)-1)/10
     # inertialist = (np.logspace(0,1,10, base=3)-1)/10
     # balancinglist = (np.logspace(0,1,10, base=3)-1)/10
-    num_cars = 100
+    num_cars = 1000
     num_delays = 10
     spreadlist = [0, 0.05, 0.1]
-    inertialist = [0, 0.2, 0.4, 0.6, 0.8]
-    balancinglist = [0, 0.01, 0.02, 0.03, 0.04]
+    inertialist = [0, 0.05, 0.1, 0.2, 0.3]
+    balancinglist = [0, 0.001, 0.002, 0.003, 0.004]
 
-    spreadlist = [0]
-    inertialist = [0, 0.2, 0.4, 0.6, 0.8]
-    balancinglist = [0]
+    # spreadlist = [0]
+    # inertialist = [0]
+    # balancinglist = [0, 0.001, 0.002, 0.003, 0.004]
 
     outputs = []
     f_orig = data['f']
@@ -236,9 +236,9 @@ if __name__ == "__main__":
     # scenario()
     import sys, random
     # myseed = random.randint(0, sys.maxint)
-    myseed = 4253647295
+    myseed = 4253648295
     print "Random seed:", myseed
     np.random.seed(myseed)
     random.seed(myseed)
-    experiment(m=10,fname='temp.pkl')
-    # experiment(m=10)
+    # experiment(m=10,fname='temp.pkl')
+    experiment(m=10)

### 2015-02-01 main.py
more output information

@@ -211,6 +211,7 @@ def experiment(m=2,fname=None):
     data['d'] = data['T'].dot(data['x_true'])
 
     with open('%s/%s' % (c.DATA_DIR,'results.txt'), 'w') as fres:
+        fres.write('spread, inertia, balancing, x flow error, x total, rest, ||Ux-f||\n')
         for f,rest,(s,i,b) in HN_data:
             # Replace f with new noisy f
             data['f'] = array(f)

### 2015-02-01 results.py
basic 3d plot

@@ -1,0 +1,63 @@
+import ipdb
+import csv
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+from mpl_toolkits.mplot3d import Axes3D
+import numpy as np
+
+import config as c
+
+class Result:
+    def __init__(self,s,i,b,x_error,x_total,rest,Uxf):
+        self.spread=float(s)
+        self.inertia=float(i)
+        self.balancing=float(b)
+        self.x_flow_error=float(x_error)
+        self.x_total=float(x_total)
+        self.rest=float(rest)
+        self.Uxf=float(Uxf)
+
+def randrange(n, vmin, vmax):
+    return (vmax-vmin)*np.random.rand(n) + vmin
+
+def plot_results(xs,ys,zs, x_label='X label', y_label='Y label',
+                     z_label='Z label', plot_label='Plot label', c='b'):
+    # ax = fig.add_subplot(111, projection='3d')
+    ax = fig.gca(projection='3d')
+    ax.plot(xs, ys, zs, 'o', c=c, marker='o', label=plot_label)
+
+    ax.set_xlabel(x_label)
+    ax.set_ylabel(y_label)
+    ax.set_zlabel(z_label)
+    # ax.legend()
+
+if __name__ == "__main__":
+    results_file = "results_4253648295_300towers.txt"
+
+    spread_results = {}
+    with open('%s/%s' % (c.DATA_DIR,results_file)) as f:
+        for row in csv.reader(f, delimiter=','):
+            s, i, b, x_error, x_total, rest, Uxf = row
+            if s == 'spread':
+                continue
+            if s in spread_results:
+                spread_results[s].append(Result(s, i, b, x_error, x_total, rest, Uxf))
+            else:
+                spread_results[s] = [Result(s, i, b, x_error, x_total, rest, Uxf)]
+
+    mpl.rcParams['legend.fontsize'] = 10
+
+    colors = ['b','g','r','c','m','y','k']
+
+    # Plot a layer for each spread level
+    fig = plt.figure()
+    for ((k,v),c) in zip(spread_results.iteritems(),colors):
+        xs,ys,zs = zip(*[(x.inertia,x.balancing,x.x_flow_error) for x in v])
+        plot_results(xs,ys,zs, x_label='Inertia', y_label='Balancing',
+                     z_label='Error', plot_label='Spread = %s' % k, c=c)
+        plt.hold(True)
+
+    plt.legend()
+    plt.show()
+    ipdb.set_trace()
+

### 2015-02-01 results.py
wireframe plot

@@ -21,10 +21,26 @@ def randrange(n, vmin, vmax):
     return (vmax-vmin)*np.random.rand(n) + vmin
 
 def plot_results(xs,ys,zs, x_label='X label', y_label='Y label',
-                     z_label='Z label', plot_label='Plot label', c='b'):
+                 z_label='Z label', plot_label='Plot label', c='b'):
     # ax = fig.add_subplot(111, projection='3d')
     ax = fig.gca(projection='3d')
     ax.plot(xs, ys, zs, 'o', c=c, marker='o', label=plot_label)
+
+    ax.set_xlabel(x_label)
+    ax.set_ylabel(y_label)
+    ax.set_zlabel(z_label)
+    # ax.legend()
+
+def plot_results_wireframe(xs,ys,zs, x_label='X label', y_label='Y label',
+                 z_label='Z label', plot_label='Plot label', c='b'):
+    # ax = fig.add_subplot(111, projection='3d')
+    ax = fig.gca(projection='3d')
+    XS,YS = sorted(list(set(xs))),sorted(list(set(ys)))
+    X,Y = np.meshgrid(XS,YS)
+    Z = np.empty_like(X)
+    for (x,y,z) in zip(xs,ys,zs):
+        Z[YS.index(y),XS.index(x)] = z
+    ax.plot_wireframe(X, Y, Z, label=plot_label, color=c)
 
     ax.set_xlabel(x_label)
     ax.set_ylabel(y_label)
@@ -48,16 +64,27 @@ if __name__ == "__main__":
     mpl.rcParams['legend.fontsize'] = 10
 
     colors = ['b','g','r','c','m','y','k']
+    spread_order = sorted(spread_results.keys())
 
     # Plot a layer for each spread level
     fig = plt.figure()
-    for ((k,v),c) in zip(spread_results.iteritems(),colors):
+    for (k,c) in zip(spread_order,colors):
+        v = spread_results[k]
         xs,ys,zs = zip(*[(x.inertia,x.balancing,x.x_flow_error) for x in v])
-        plot_results(xs,ys,zs, x_label='Inertia', y_label='Balancing',
+        plot_results_wireframe(xs,ys,zs, x_label='Inertia', y_label='Balancing',
                      z_label='Error', plot_label='Spread = %s' % k, c=c)
         plt.hold(True)
-
     plt.legend()
+
+    fig = plt.figure()
+    for (k,c) in zip(spread_order,colors):
[…]

### 2015-02-01 results.py
plots for % error from rest, and % in dictionary error

@@ -31,10 +31,9 @@ def plot_results(xs,ys,zs, x_label='X label', y_label='Y label',
     ax.set_zlabel(z_label)
     # ax.legend()
 
-def plot_results_wireframe(xs,ys,zs, x_label='X label', y_label='Y label',
+def plot_results_wireframe(ax,xs,ys,zs, x_label='X label', y_label='Y label',
                  z_label='Z label', plot_label='Plot label', c='b'):
     # ax = fig.add_subplot(111, projection='3d')
-    ax = fig.gca(projection='3d')
     XS,YS = sorted(list(set(xs))),sorted(list(set(ys)))
     X,Y = np.meshgrid(XS,YS)
     Z = np.empty_like(X)
@@ -68,20 +67,21 @@ if __name__ == "__main__":
 
     # Plot a layer for each spread level
     fig = plt.figure()
+    plt1 = fig.add_subplot(1,3,1,projection='3d')
+    plt2 = fig.add_subplot(1,3,2,projection='3d')
+    plt3 = fig.add_subplot(1,3,3,projection='3d')
     for (k,c) in zip(spread_order,colors):
         v = spread_results[k]
-        xs,ys,zs = zip(*[(x.inertia,x.balancing,x.x_flow_error) for x in v])
-        plot_results_wireframe(xs,ys,zs, x_label='Inertia', y_label='Balancing',
-                     z_label='Error', plot_label='Spread = %s' % k, c=c)
-        plt.hold(True)
-    plt.legend()
-
-    fig = plt.figure()
-    for (k,c) in zip(spread_order,colors):
-        v = spread_results[k]
-        xs,ys,zs = zip(*[(x.inertia,x.balancing,x.x_flow_error) for x in v])
-        plot_results(xs,ys,zs, x_label='Inertia', y_label='Balancing',
-                            z_label='Error', plot_label='Spread = %s' % k, c=c)
+        xs,ys,z1s,z2s = zip(*[(x.inertia,x.balancing,x.x_flow_error,
+                               x.rest/x.x_total) for x in v])
+        z3s = [b-a for (a,b) in zip(z1s,z2s)]
+        # ax = fig.gca(projection='3d')
+        plot_results_wireframe(plt1,xs,ys,z1s, x_label='Inertia', y_label='Balancing',
+                     z_label='% flow error', plot_label='Spread = %s' % k, c=c)
+        plot_results_wireframe(plt2,xs,ys,z2s, x_label='Inertia', y_label='Balancing',
[…]

### 2015-02-02 main.py
experiment 2 results

@@ -189,7 +189,7 @@ def experiment(m=2,fname=None):
     num_delays = 10
     spreadlist = [0, 0.05, 0.1]
     inertialist = [0, 0.05, 0.1, 0.2, 0.3]
-    balancinglist = [0, 0.001, 0.002, 0.003, 0.004]
+    balancinglist = [0, 0.0005, 0.001, 0.002, 0.003]
 
     # spreadlist = [0]
     # inertialist = [0]

### 2015-02-02 paper/conclusion.tex
saving x_true,x_est,f with output; adding paper template

%!TEX root = main.tex

\section{Conclusion}
The conclusion goes here.

### 2015-02-02 paper/experiments.tex
saving x_true,x_est,f with output; adding paper template

%!TEX root = main.tex

\section{Experiments and numerical results}

### 2015-02-02 paper/intro.tex
saving x_true,x_est,f with output; adding paper template

%!TEX root = main.tex

\section{Introduction}
In this work, we study the noise sensitivity of the state-of-the-art for route flow estimation. Route flow estimation on road networks is an important problem for mobility cyber-physical systems (CPS), as any prediction and control applications require accurate and reliable estimates of the current state of the road network. Previous work has demonstrated the promise of using cellular towers as sensor inputs to a convex optimization formulation of the problem, along with a projected first-order method that scales well to full-sized city networks [cite ISTTT]. However, the work uses entirely synthetic data which assumes that vehicles are connected to the closest cell tower throughout their trajectories (i.e. voronoi partitions). In

### 2015-02-02 paper/model.tex
saving x_true,x_est,f with output; adding paper template

--- 2015-02-01 model.tex
@@
-\documentclass[twocolumn,10pt]{article}
-\usepackage{amsmath}
-
-\begin{document}
+%!TEX root = main.tex
 
@@
 $P_{hyst}$ represents an amount of hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers: \begin{equation}
-  P_{hyst_{v-t}} = \begin{cases}
+  P_{hyst_{v-t}} = \begin{dcases}
     \beta & \mathrm{if~} v \mathrm{~is~already~connected~to~} t, \\
     0 & \mathrm{otherwise.}
-  \end{cases}
+  \end{dcases}
 \end{equation}
@@
 The units are arbitrarily scaled, and so require manual tuning to determine appropriate relative weights.
-
-\end{document}

### 2015-02-02 helpers.py

@@ -126,7 +126,7 @@ def update_args(args, params):
     return args
 
 def experiment_LS(args, test=None, data=None, full=True, L=True, OD=True,
-                  CP=True, LP=True, eq='CP', init=True, noisy=False):
+                  CP=True, LP=True, eq='CP', init=True, noisy=False, save_x=False):
     """
     Least squares experiment
     :param test:
@@ -162,12 +162,14 @@ def experiment_LS(args, test=None, data=None, full=True, L=True, OD=True,
         iters, times, states = [0],[0],[x0]
         x_last, error, output = LS_postprocess(states,x0,A,b,x_true,scaling=flow,
                                                block_sizes=block_sizes,N=N,
-                                               output=output,is_x=True)
+                                               output=output,is_x=True,
+                                               save_x=save_x)
     else:
         iters, times, states = LS_solve(A,b,x0,N,block_sizes,args)
         x_last, error, output = LS_postprocess(states,x0,A,b,x_true,scaling=flow,
                                                block_sizes=block_sizes,N=N,
-                                               output=output)
+                                               output=output,
+                                               save_x=save_x)
 
     # LS_plot(x_last, times, error)
     output['duration'] = np.sum(times)
@@ -228,7 +230,7 @@ def LS_solve(A,b,x0,N,block_sizes,args):
     return iters, times, states
 
 def LS_postprocess(states, x0, A, b, x_true, scaling=None, block_sizes=None,
-                   output=None, N=None, is_x=False):
+                   output=None, N=None, is_x=False, rest=0, save_x=False):
     if scaling is None:
         scaling = np.ones(x_true.shape)
     if output is None:
@@ -288,6 +290,10 @@ def LS_postprocess(states, x0, A, b, x_true, scaling=None, block_sizes=None,
     start_dist_from_true = np.max(scaling * np.abs(x_true-x0))
     logging.debug('max|f * (x_init-x_true)|: %.5f' % start_dist_from_true)
     output['max|f * (x_init-x_true)|'] = start_dist_from_true
+
+    if save_x is True:
+        output['x_est'] = x_last
+        output['x_true'] = x_true
 
     return x_last, error, output
 

### 2015-02-02 main.py

@@ -107,12 +107,13 @@ def scenario(params=None,m=2):
 
     return args, data, graph
 
-def solve(args, data, noisy=False):
+def solve(args, data, noisy=False, save_x=False):
     eq = 'CP' if args.use_CP else 'OD'
     if args.solver == 'LS':
         output = experiment_LS(args, full=args.all_links, init=args.init,
                                L=args.use_L, OD=args.use_OD, CP=args.use_CP,
-                               LP=args.use_LP, eq=eq, data=data, noisy=noisy)
+                               LP=args.use_LP, eq=eq, data=data, noisy=noisy,
+                               save_x=save_x)
     elif args.solver == 'LSQR':
         output = experiment_LSQR(args, full=args.all_links, L=args.use_L,
                                  OD=args.use_OD, CP=args.use_CP, LP=args.use_LP,
@@ -189,7 +190,7 @@ def experiment(m=2,fname=None):
     num_delays = 10
     spreadlist = [0, 0.05, 0.1]
     inertialist = [0, 0.05, 0.1, 0.2, 0.3]
-    balancinglist = [0, 0.0005, 0.001, 0.002, 0.003]
+    balancinglist = [0, .0004, .0008, .0012, .002] # [0, 0.0005, 0.001, 0.002, 0.003]
 
     # spreadlist = [0]
     # inertialist = [0]
@@ -210,13 +211,20 @@ def experiment(m=2,fname=None):
     data['b'] = data['A'].dot(data['x_true'])
     data['d'] = data['T'].dot(data['x_true'])
 
+    delimiter = "|"
+    captions = ['spread', 'inertia', 'balancing', 'x flow error', 'x total',
+                'rest', 'Ux-f', 'x flow error in dict', 'x_true', 'x_est', 'f']
+    formats = ['%0.8f', '%0.8f', '%0.8f', '%0.8f', '%0.8f', '%0.8f', '%0.8f',
+               '%0.8f', '%s', '%s', '%s']
+    format_string = delimiter.join(formats)
+
     with open('%s/%s' % (c.DATA_DIR,'results.txt'), 'w') as fres:
-        fres.write('spread, inertia, balancing, x flow error, x total, rest, ||Ux-f||\n')
+        fres.write('%s\n' % delimiter.join(captions))
         for f,rest,(s,i,b) in HN_data:
             # Replace f with new noisy f
             data['f'] = array(f)
             # ipdb.set_trace()
-            output = solve(args, data, noisy=True)
+            output = solve(args, data, noisy=True, save_x=True)
[…]

### 2015-02-02 results.py

@@ -6,9 +6,11 @@ from mpl_toolkits.mplot3d import Axes3D
 import numpy as np
 
 import config as c
+from helpers import array
 
 class Result:
-    def __init__(self,s,i,b,x_error,x_total,rest,Uxf):
+    def __init__(self,s,i,b,x_error,x_total,rest,Uxf,x_error_indict=None,
+                 x_true=None,x_est=None,f=None):
         self.spread=float(s)
         self.inertia=float(i)
         self.balancing=float(b)
@@ -16,6 +18,10 @@ class Result:
         self.x_total=float(x_total)
         self.rest=float(rest)
         self.Uxf=float(Uxf)
+        self.x_error_indict=float(x_error_indict)
+        self.x_true=array(np.fromstring(x_true[1:-1], sep=' '))
+        self.x_est=array(np.fromstring(x_est[1:-1], sep=' '))
+        self.f=array(np.fromstring(f[1:-1], sep=' '))
 
 def randrange(n, vmin, vmax):
     return (vmax-vmin)*np.random.rand(n) + vmin
@@ -48,6 +54,7 @@ def plot_results_wireframe(ax,xs,ys,zs, x_label='X label', y_label='Y label',
 
 if __name__ == "__main__":
     results_file = "results_4253648295_300towers.txt"
+    # results_file = "results.txt"
 
     spread_results = {}
     with open('%s/%s' % (c.DATA_DIR,results_file)) as f:
@@ -55,10 +62,26 @@ if __name__ == "__main__":
             s, i, b, x_error, x_total, rest, Uxf = row
             if s == 'spread':
                 continue
+            r = Result(s, i, b, x_error, x_total, rest, Uxf)
             if s in spread_results:
-                spread_results[s].append(Result(s, i, b, x_error, x_total, rest, Uxf))
+                spread_results[s].append(r)
             else:
-                spread_results[s] = [Result(s, i, b, x_error, x_total, rest, Uxf)]
+                spread_results[s] = [r]
+
+    # FOR NEW EXPERIMENTS (new data format)
+    # with open('%s/%s' % (c.DATA_DIR,results_file)) as f:
+    #     for row in csv.reader(f, delimiter='|'):
+    #         print row
+    #         s, i, b, x_error, x_total, rest, Uxf, x_error_indict, x_true, x_est, f = row
+    #         if s == 'spread':
+    #             continue
+    #         r = Result(s, i, b, x_error, x_total, rest, Uxf,
[…]

### 2015-02-02 paper/intro.tex
+ bibliography

@@
 \section{Introduction}
-In this work, we study the noise sensitivity of the state-of-the-art for route flow estimation.
-Route flow estimation on road networks is an important problem for mobility cyber-physical systems (CPS), as any prediction and control applications require accurate and reliable estimates of the current state of the road network.
-Previous work has demonstrated the promise of using cellular towers as sensor inputs to a convex optimization formulation of the problem, along with a projected first-order method that scales well to full-sized city networks [cite ISTTT].
+In this work, we study the noise sensitivity of the state-of-the-art for route flow estimation for mobility cyber-physical systems (CPS).
+Route flow estimation on road networks is a critical problem for mobility CPS, as any prediction and control applications require accurate and reliable estimates of the state of the road network.
+Previous work has demonstrated the promise of using cellular towers as sensor inputs to a convex optimization formulation of the problem, along with a projected first-order method that scales well to large city-scale networks \cite{Wu2015}.
 However, the work uses entirely synthetic data which assumes that vehicles are connected to the closest cell tower throughout their trajectories (i.e.

### 2015-02-02 paper/experiments.tex
experiment 1 take 2 results; +plotting switch; some paper updates including references

@@
 \section{Experiments and numerical results}
+
+sparse setup + dense setup (in terms of cells, e.g. city center vs rural area)
+
+“sparser”: smallest number of cell towers for which route flow accuracy is pretty good ($<5\%$ error); hopefully somewhat robust to handoff model
+
+“city center”: super dense number of cell towers; handoff model should cause tons of problems here quickly
+
+Motivated by the growth of mobile technology usage and penetration rate, \cite{}

### 2015-02-02 paper/intro.tex
experiment 1 take 2 results; +plotting switch; some paper updates including references

@@
 In this work, we study the noise sensitivity of the state-of-the-art for route flow estimation for mobility cyber-physical systems (CPS).
-Route flow estimation on road networks is a critical problem for mobility CPS, as any prediction and control applications require accurate and reliable estimates of the state of the road network.
-Previous work has demonstrated the promise of using cellular towers as sensor inputs to a convex optimization formulation of the problem, along with a projected first-order method that scales well to large city-scale networks \cite{Wu2015}.
-However, the work uses entirely synthetic data which assumes that vehicles are connected to the closest cell tower throughout their trajectories (i.e.
-voronoi partitions).
-In
+Route flow estimation on road networks is a critical problem for mobility CPS, as any real-time prediction and control applications require accurate and reliable estimates of the state of the road network.
+Previous work has demonstrated the promise of using area-based sensors such as cellular towers as inputs to a convex optimization formulation of the problem, along with a projected first-order method that scales well to large city-scale networks \cite{Wu2015}.
+However, the numerical results are based off of entirely synthetic data, which makes the strong but common assumption that vehicles are connected to the closest cell tower throughout their trajectory (i.e.
+voronoi tessellations) \cite{Voronoi1908}.
+The real world is seldom so kind.
+
+We extend upon the previous work by analyzing the sensitivity of the estimation procedure to structured noise.
+In particular, we consider noise from a generative model based off of a handoff model for cellular base stations, which .
+
+\subsection{Motivation and related works}
+
+\subsection{Route flow estimation problem}
+
+(include Jerome’s diagram here)

### 2015-02-02 results.py

@@ -55,33 +55,33 @@ def plot_results_wireframe(ax,xs,ys,zs, x_label='X label', y_label='Y label',
 if __name__ == "__main__":
     results_file = "results_4253648295_300towers.txt"
     # results_file = "results.txt"
+    results_file = 'results_4253648295_300towers_take2.txt'
 
     spread_results = {}
-    with open('%s/%s' % (c.DATA_DIR,results_file)) as f:
-        for row in csv.reader(f, delimiter=','):
-            s, i, b, x_error, x_total, rest, Uxf = row
-            if s == 'spread':
-                continue
-            r = Result(s, i, b, x_error, x_total, rest, Uxf)
-            if s in spread_results:
-                spread_results[s].append(r)
-            else:
-                spread_results[s] = [r]
-
-    # FOR NEW EXPERIMENTS (new data format)
     # with open('%s/%s' % (c.DATA_DIR,results_file)) as f:
-    #     for row in csv.reader(f, delimiter='|'):
-    #         print row
-    #         s, i, b, x_error, x_total, rest, Uxf, x_error_indict, x_true, x_est, f = row
+    #     for row in csv.reader(f, delimiter=','):
+    #         s, i, b, x_error, x_total, rest, Uxf = row
     #         if s == 'spread':
     #             continue
-    #         r = Result(s, i, b, x_error, x_total, rest, Uxf,
-    #                    x_error_indict=x_error_indict, x_true=x_true,
-    #                    x_est=x_est, f=f)
+    #         r = Result(s, i, b, x_error, x_total, rest, Uxf)
     #         if s in spread_results:
     #             spread_results[s].append(r)
     #         else:
     #             spread_results[s] = [r]
+
+    # FOR NEW EXPERIMENTS (new data format)
+    with open('%s/%s' % (c.DATA_DIR,results_file)) as f:
+        for row in csv.reader(f, delimiter='|'):
+            s, i, b, x_error, x_total, rest, Uxf, x_error_indict, x_true, x_est, f = row
+            if s == 'spread':
+                continue
+            r = Result(s, i, b, x_error, x_total, rest, Uxf,
+                       x_error_indict=x_error_indict, x_true=x_true,
+                       x_est=x_est, f=f)
+            if s in spread_results:
+                spread_results[s].append(r)
+            else:
+                spread_results[s] = [r]
 
[…]

### 2015-02-02 paper/experiments.tex
figures; intro and problem statement

@@
 
-sparse setup + dense setup (in terms of cells, e.g. city center vs rural area)
+\subsection{Experimental setup}
+\begin{figure}[h!]
+  \centering
+    \includegraphics[width=0.47\textwidth]{figures/small_map_half.jpeg}
+  \caption{\footnotesize{Benchmark example network based off of the Highway network of the I-210 highway corridor in L.A.
+county (top, from Google Maps); Network with 80 sampled cells, with a higher concentration of cells near downtown (bottom).
+A random path from is shown in red with the closest cell towers.}}
+  \label{fig:small-network}
+\end{figure}
+
+We consider a medium sized network and the following scenarios
+\begin{itemize}
+\item \textbf{???} ($N=375$):
+\item \textbf{City Center} ($N=375$): We emulate a popular commercial district with a dense sampling of cellular towers.
+\end{itemize}
+
+\subsection{Results}
 
@@
 “city center”: super dense number of cell towers; handoff model should cause tons of problems here quickly
-
-Motivated by the growth of mobile technology usage and penetration rate, \cite{}

### 2015-02-02 paper/intro.tex
figures; intro and problem statement

@@
 Previous work has demonstrated the promise of using area-based sensors such as cellular towers as inputs to a convex optimization formulation of the problem, along with a projected first-order method that scales well to large city-scale networks \cite{Wu2015}.
-However, the numerical results are based off of entirely synthetic data, which makes the strong but common assumption that vehicles are connected to the closest cell tower throughout their trajectory (i.e.
-voronoi tessellations) \cite{Voronoi1908}.
+Importantly, the work's introduction of the concept of \textit{cellpath} (sequences of cell tower regions) helps to cope with the underdetermined-ness of the problem.
+However, the numerical results are based off of noiseless synthetic data, which makes the strong but common assumption that vehicles are connected to the closest cell tower throughout their trajectory (i.e.
+voronoi tessellations of cell tower regions) \cite{Voronoi1908}.
 The real world is seldom so kind.
@@
 We extend upon the previous work by analyzing the sensitivity of the estimation procedure to structured noise.
-In particular, we consider noise from a generative model based off of a handoff model for cellular base stations, which .
-
-\subsection{Motivation and related works}
+In particular, we consider noise from a generative model based off of a handoff model for cellular base stations, which includes hysteresis margins for handoffs, load balancing, and random interference.
 
 \subsection{Route flow estimation problem}
+The route flow estimation problem (illustrated in Figure \ref{fig:example-setup}) is as follows: for a road network $G=(V,E)$, let $\mathcal{R}$ denote the set of $n$ routes that vehicles take.
+We denote $f$ to be the cellpath flow (measured), $d$ to be the origin-destination (OD) flow (measured), $b$ the link flow (measured), and $x \in \mathbb{R}^n$ the route flow (unknown).
+We are given the linear operators relating the sensor measurements ($f,d,b$) to the route flow $x$ ($U,T,A$, respectively), that is $Ax=b, Tx=d, Ux=f$.
+We wish to recover $x$ from the flow measurements of the sensors.
 
-(include Jerome’s diagram here)
+With the exception of the noise model, we follow the same assumptions as in \cite{Wu2015}: static setting, and continuous and well-posed cellpaths.
+
+\begin{figure}[h!]
+  \centering
+    \includegraphics[width=0.47	\textwidth]{figures/setup}
+  \caption{\footnotesize{In this illustration, we have two origins A and C ({\color{blue}blue}) and one destination B ({\color{red}red}).
+We have routes $r_1,r_2,r_3,r_4$ with flows $x=(x_1,x_2,x_3, x_4)$ such that $r_1,r_2$ go from A to B and $r_3,r_4$ go from C to B.
+Cells $c_1,\cdots,c_7$ are shown in {\color{magenta} purple} dashed regions.
+Since route $r_1$ goes through cells $c_1,c_2,c_3,c_4$, its associated cellpath is $p_{1234}$.
+Similarly, routes $r_2,r_3,r_4$ have cellpaths $p_{1654},p_{654},p_{654}$ respectively.
+Let $f_{p1234},\,f_{p1654},\,f_{p654}$ be the cellpath flows (obtained from cellular network data), \emph{i.e.} there are $f_{p1234}$=1000~veh/h going through $c_1,c_2,c_3,c_4$.
+Let $d_{AB}$ and $d_{CB}$ be the OD demands and $b$ be the link flow ({\color{green}green}, from loop detectors).
+Without considering data from cellpaths, the problem has \emph{one degree of freedom} and is \emph{underdetermined} with only the OD demands as data.}}
+  \label{fig:example-setup}
+\end{figure}
+
+\subsection{Related works}

### 2015-02-02 main.py

@@ -262,5 +262,5 @@ if __name__ == "__main__":
     print "Random seed:", myseed
     np.random.seed(myseed)
     random.seed(myseed)
-    experiment(m=10,fname='temp.pkl')
-    # experiment(m=10)
+    # experiment(m=10,fname='temp.pkl')
+    experiment(m=10)

### 2015-02-02 paper/experiments.tex
results for experiment 2 take 2, some paper edits

@@
 
-We consider a medium sized network and the following scenarios
+We consider a medium sized network based off of the I-210 highway corridor in Los Angeles (see Figure \ref{fig:small-network}) in the following scenarios
 \begin{itemize}
-\item \textbf{???} ($N=375$):
-\item \textbf{City Center} ($N=375$): We emulate a popular commercial district with a dense sampling of cellular towers.
+\item \textit{Urban sprawl} ($N=300$): We emulate a city network where the density of cell towers is sufficient for recovering route flow in the noiseless setting.
+\item \textit{City Center} ($N=375$): We emulate a popular commercial district with a dense sampling of cellular towers.
 \end{itemize}

### 2015-02-02 paper/experiments.tex
results

@@
 
-We consider a medium sized network based off of the I-210 highway corridor in Los Angeles (see Figure \ref{fig:small-network}) in the following scenarios
+We consider a medium sized network based off of the I-210 highway corridor in Los Angeles, CA (see Figure \ref{fig:small-network}) in the following scenarios, where $N$ indicates the number of uniformly sampled cellular tower positions.
 \begin{itemize}
 \item \textit{Urban sprawl} ($N=300$): We emulate a city network where the density of cell towers is sufficient for recovering route flow in the noiseless setting.
-\item \textit{City Center} ($N=375$): We emulate a popular commercial district with a dense sampling of cellular towers.
+\item \textit{City Center} ($N=375$): We emulate a popular commercial district with a very dense sampling.
 \end{itemize}
+In each of the scenarios, we first compute a feasible route flow $x$ for the user equilibrium solution of the network.
+Treating $x$ as our sampling distribution, we issue 10,000 vehicles and collect the cellpath flow following the noise model described in Section \ref{sec:system-model}.
+We fix the parameters $\alpha\in\set{0,0.05,0.1}, \beta=\set{0, 0.05, 0.1, 0.2, 0.3},\xi=\set{0, .0004, .0008, .0012, .002}$.
+For each configuration, we use the projected first-order method solver in \cite{Wu2015} to compute $x_{est}$.
+We evaluate on the metric $\norm{x-x_{est}}_1/\norm{x}_1$, which corresponds to the percent route flow error.
 
-\subsection{Results}
+\subsection{Preliminary results}
+
+We present preliminary numerical results in Figure \ref{fig:results1}.
+
+\begin{figure}[h!]
+  \centering
+    \includegraphics[width=0.47\textwidth]{figures/results_300_hysteresis.png}
+  \caption{\footnotesize{This plot show the initial findings for $N=300$.
+In general, the percent route flow error increases as the interference increases.
+The percent route flow error first increase then decreases as the hysteresis margin is increased.
+The load balancing parameter indicates positive correlation with percent route flow error.}}
+  \label{fig:results1}
+\end{figure}
 

### 2015-02-02 paper/model.tex
results

@@
 
-\subsection{System model}
+\section{System model for handoff noise}
+\label{sec:system-model}
 This work models the assignment of individual vehicles to cell towers with an effective received signal strength (eRSS) based decision process.

### 2015-02-02 main.py

@@ -246,6 +246,7 @@ def experiment(m=2,fname=None):
                                          np.array_str(x_est,max_line_width=np.Inf),
                                          np.array_str(f,max_line_width=np.Inf))
             fres.write('%s\n' % write_out)
+            ipdb.set_trace()
 
     ipdb.set_trace()
     # return output_control, outputs
@@ -262,5 +263,5 @@ if __name__ == "__main__":
     print "Random seed:", myseed
     np.random.seed(myseed)
     random.seed(myseed)
-    # experiment(m=10,fname='temp.pkl')
-    experiment(m=10)
+    experiment(m=10,fname='temp.pkl')
+    # experiment(m=10)

### 2015-02-02 results.py

@@ -51,11 +51,12 @@ def plot_results_wireframe(ax,xs,ys,zs, x_label='X label', y_label='Y label',
     ax.set_ylabel(y_label)
     ax.set_zlabel(z_label)
     # ax.legend()
+    ipdb.set_trace()
 
 if __name__ == "__main__":
     results_file = "results_4253648295_300towers.txt"
     # results_file = "results.txt"
-    results_file = 'results_4253648295_300towers_take2.txt'
+    results_file = 'results_4253648295_375towers_take2.txt'
 
     spread_results = {}
     # with open('%s/%s' % (c.DATA_DIR,results_file)) as f:
@@ -90,19 +91,20 @@ if __name__ == "__main__":
 
     # Plot a layer for each spread level
     fig = plt.figure()
-    plt1 = fig.add_subplot(1,2,1,projection='3d')
-    plt2 = fig.add_subplot(1,2,2,projection='3d')
+    plt1 = fig.add_subplot(1,1,1,projection='3d')
+    # plt2 = fig.add_subplot(1,2,2,projection='3d')
     for (k,c) in zip(spread_order,colors):
         v = spread_results[k]
         xs,ys,z1s,z2s = zip(*[(x.inertia,x.balancing,x.x_flow_error,
                                x.x_error_indict) for x in v])
         # ax = fig.gca(projection='3d')
-        plot_results_wireframe(plt1,xs,ys,z1s, x_label='Inertia', y_label='Balancing',
-                     z_label='% flow error', plot_label='Spread = %s' % k, c=c)
-        plot_results_wireframe(plt2,xs,ys,z2s, x_label='Inertia', y_label='Balancing',
-                               z_label='% dist error', plot_label='Spread = %s' % k, c=c)
+        plot_results_wireframe(plt1,xs,ys,z1s, x_label='Hysteresis', y_label='Load balancing',
+                     z_label='% flow error', plot_label='Interference = %s' % k, c=c)
+        # plot_results_wireframe(plt2,xs,ys,z2s, x_label='Hysteresis', y_label='Load balancing',
+        #                        z_label='% dist error', plot_label='Interference = %s' % k, c=c)
         plt.hold(True)
     plt.legend()
+    plt.title('% Route flow error under handoff noise model')
 
     plt.show()
     ipdb.set_trace()

### 2015-02-02 paper/experiments.tex
prelim results; corref computation

@@
 
-We present preliminary numerical results in Figure \ref{fig:results1}.
+We present preliminary numerical results in Figure \ref{fig:results1} (omitting the denser experiment due to space limitations).
+In both experiments, there is a strong positive correlation ($R=0.78$ and $R=0.74$, respectively) between the load balancing gain and percent error.
+In the first experiment, the hysteresis margin gain causes an interesting change in route flow error, first increasing then decreasing, in the presence of other types of noise.
+We suspect the decrease in percent error is a side effect of the delay in switching cell towers when a vehicle moves by decreasing the chance of connecting to an incorrect tower.
+In the denser experiment, the route flow error is much more sensitive to the hysteresis margin gain, which can be explained by switching delays resulting in entirely missed cells, as the vehicle traverses its trajectory.
 
@@
 \end{figure}
-
-“sparser”: smallest number of cell towers for which route flow accuracy is pretty good ($<5\%$ error); hopefully somewhat robust to handoff model
-
-“city center”: super dense number of cell towers; handoff model should cause tons of problems here quickly

### 2015-02-02 results.py

@@ -51,7 +51,9 @@ def plot_results_wireframe(ax,xs,ys,zs, x_label='X label', y_label='Y label',
     ax.set_ylabel(y_label)
     ax.set_zlabel(z_label)
     # ax.legend()
-    ipdb.set_trace()
+    print plot_label
+    print 'Corrcoef (balancing): %s' % np.corrcoef(Y.flatten(),Z.flatten())[0][1]
+    print 'Corrcoef (inertia): %s' % np.corrcoef(X.flatten(),Z.flatten())[0][1]
 
 if __name__ == "__main__":
     results_file = "results_4253648295_300towers.txt"
@@ -71,6 +73,13 @@ if __name__ == "__main__":
     #             spread_results[s] = [r]
 
     # FOR NEW EXPERIMENTS (new data format)
+    with open('%s/%s' % (c.DATA_DIR,results_file)) as f:
+        blah = [row[:4] for row in csv.reader(f, delimiter='|')][1:]
+        s,i,b,x_error = zip(*blah)
+        print np.corrcoef(array(s).astype(np.float),array(x_error).astype(np.float))[0][1]
+        print np.corrcoef(array(i).astype(np.float),array(x_error).astype(np.float))[0][1]
+        print np.corrcoef(array(b).astype(np.float),array(x_error).astype(np.float))[0][1]
+
     with open('%s/%s' % (c.DATA_DIR,results_file)) as f:
         for row in csv.reader(f, delimiter='|'):
             s, i, b, x_error, x_total, rest, Uxf, x_error_indict, x_true, x_est, f = row

### 2015-02-02 paper/conclusion.tex
experiment 1 take 2 results; +plotting switch; some paper updates including references
conclusion

@@
 \section{Conclusion}
-The conclusion goes here.
+We studied the problem of route flow estimation from the perspective of a sensitivity analysis, using a structured noise model based off of communication network handoff algorithms.
+We presented our preliminary results on the effect of the structured noise on the recovery of route flow, and we plan to continue this analysis with more extensive trials.
+This work is in preparation for a full-scale run of the route flow estimation on cellular signaling data from AT\&T in the greater Los Angeles area.
+We additionally plan to investigate a sensitivity analysis for the dynamic route flow estimation problem, and we plan to use our handoff model to augment our prior on vehicle connectivity.
+
+% Multiple cellpaths per route

### 2015-02-02 paper/intro.tex
results
revised intro

--- 2015-02-02 paper/intro.tex
@@
 \section{Introduction}
-In this work, we study the noise sensitivity of the state-of-the-art for route flow estimation for mobility cyber-physical systems (CPS).
-Route flow estimation on road networks is a critical problem for mobility CPS, as any prediction and control applications require accurate and reliable estimates of the state of the road network.
-Previous work has demonstrated the promise of using cellular towers as sensor inputs to a convex optimization formulation of the problem, along with a projected first-order method that scales well to large city-scale networks \cite{Wu2015}.
-However, the work uses entirely synthetic data which assumes that vehicles are connected to the closest cell tower throughout their trajectories (i.e.
-voronoi partitions).
-In
+Route flow estimation on road networks is a critical problem for mobility CPS, as real-time prediction and control applications require the state of the road network.
+Previous work has demonstrated the promise of computing an estimate from area-based sensors such as cellular towers, using a projected first-order method that scales well to large city-scale networks \cite{Wu2015}.
+Importantly, the work's introduction of \textit{cellpaths} -- cell tower connection sequences -- helps to cope with the underdetermined-ness of the problem.
+However, previous analysis has been based off of noiseless synthesized data, which makes the strong but common assumption that vehicles are connected to the closest cell tower throughout their trajectory (i.e.
+voronoi tessellations of cell tower regions) \cite{Voronoi1908}.
+The real world is seldom so kind.
+
+In this work we analyze the sensitivity of the flow estimation procedure to structured noise.
+In particular, we consider the effect of a handoff model for within the cellular network, which includes hysteresis margins for handoffs and cell tower load balancing, in the presence of RF interference.

### 2015-02-02 paper/model.tex
revised intro

--- 2015-02-02 paper/model.tex
@@
 
-\subsection{System model}
+\section{Problem formulation}
+\label{sec:system-model}
+
+\subsection{Route flow estimation}
+The route flow estimation problem (illustrated in Fig.~\ref{fig:example-setup}) is as follows: for a road network $G=(V,E)$, let $\mathcal{R}$ denote the set of $n$ routes that vehicles take.
+The route flow $x \in \mathbb{R}^n$ is the unknown state of the road network.
+We employ sensor measurments cellpath flow $f$, origin-destination (OD) flow $d$, and link flow $b$.
+We are given the linear operators $U, T, A$ relating the sensor measurements to the route flow $x$, that is, $Ax=b, Tx=d, Ux=f$.
+We wish to estimate the state $x$ from the sensor data $f,d,b$.
+
+With the exception of the noise model, we follow the same assumptions as in \cite{Wu2015}: static setting, and continuous and well-posed cellpaths.
+
+\begin{figure}[htb]
+  \centering
+    \includegraphics[width=0.47	\textwidth]{figures/setup}
+  \caption{\footnotesize{In this illustration, we have two origins A and C ({\color{blue}blue}) and one destination B ({\color{red}red}).
+We have routes $r_1,r_2,r_3,r_4$ with flows $x=(x_1,x_2,x_3, x_4)$ such that $r_1,r_2$ go from A to B and $r_3,r_4$ go from C to B.
+Cells $c_1,\cdots,c_7$ are shown in {\color{magenta} purple} dashed regions.
+Since route $r_1$ goes through cells $c_1,c_2,c_3,c_4$, its associated cellpath is $p_{1234}$.
+Similarly, routes $r_2,r_3,r_4$ have cellpaths $p_{1654},p_{654},p_{654}$ respectively.
+Let $f_{p1234},\,f_{p1654},\,f_{p654}$ be the cellpath flows (obtained from cellular network data), \emph{i.e.} there are $f_{p1234}$=1000~veh/h going through $c_1,c_2,c_3,c_4$.
+Let $d_{AB}$ and $d_{CB}$ be the OD demands and $b$ be the link flow ({\color{green}green}, from loop detectors).
+Without considering data from cellpaths, the problem has \emph{one degree of freedom} and is \emph{underdetermined} with only the OD demands as data.}}
+  \label{fig:example-setup}
+\end{figure}
+
+\subsection{Cell tower handoff noise model}
+
 This work models the assignment of individual vehicles to cell towers with an effective received signal strength (eRSS) based decision process.
@@
 each vehicle gets assigned to the cell tower with the highest eRSS value at each time point in the simulation.
-All towers are assumed to output with the same transmit power, so eRSS can be calculated in dB as: \begin{eqnarray}
+
+\begin{eqnarray}
   eRSS_{v-t} & = & \left( \frac{P_{RX_v}}{P_{TX_t}} \right)_{dB} 
                    + P_{handoff_{v-t}} \\
-  & = & P_{d_{v-t}} +P_{int} + P_{hyst_{v-t}} + P_{load_t}.
+  & = & P_{d_{v-t}} +P_{int} + P_{hyst_{v-t}} + P_{load_t}, \\
+  P_{d_{v-t}} & = & -10 \gamma \log_{10} d_{v-t}, \\
+  P_{int} & = & -\alpha \cdot \mathrm{Unif}(0,1). \\
+  P_{hyst_{v-t}} & = & \begin{dcases}
+    \beta & \mathrm{if~} v \mathrm{~is~already~connected~to~} t, \\
+    0 & \mathrm{otherwise,}
+  \end{dcases} \\
+  P_{load_t} & = & -\xi \cdot N_{t}.
 \end{eqnarray}
 
-In this equation, the actual received signal strength is composed of two parts, $P_d$ and $P_{int}$.  The attenuation due to path loss is given by: \begin{equation}
-  P_{d_{v-t}} = -10 \gamma \log_{10} d_{v-t},
-\end{equation}
-where $d_{v-t}$ is the distance between the vehicle and the cell tower, and $\gamma$ is the path loss exponent.
-The additional attenuation due to interference, multipath effects, and other RF noise is wrapped up into a uniformly distributed random penalty: \begin{equation}
-  P_{int} = -\alpha \cdot \mathrm{Unif}(0,1).
-\end{equation}
+In this equation, the actual received signal strength is attenuated by two sources: the path loss $P_d$ 
+is a function of the distance between the vehicle and the cell tower $d_{v-t}$ and path loss exponent $\gamma$, while 
+interference, multipath effects, and other RF noise are wrapped up into a uniformly distributed random penalty $P_{int}$.
 
 The dynamics of the tower handoff, $P_{handoff}$, are modelled using two parameters.
-$P_{hyst}$ represents an amount of hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers: \begin{equation}
-  P_{hyst_{v-t}} = \begin{dcases}
-    \beta & \mathrm{if~} v \mathrm{~is~already~connected~to~} t, \\
-    0 & \mathrm{otherwise.}
-  \end{dcases}
-\end{equation}
-$P_{load}$ represents the load balancing efforts to distribute usage across the cell network, adding an eRSS penalty to heavily loaded towers: \begin{equation}
-  P_{load_t} = -\xi \cdot N_{t},
-\end{equation}
+$P_{hyst}$ represents an amount of hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers.
+$P_{load}$ represents the load balancing efforts to distribute usage across the cell network, adding an eRSS penalty to heavily loaded towers.
+
 where $N_t$ is the number of other vehicles already connected to tower $t$.

### 2015-02-02 paper/model.tex
revising model.tex

@@
 
+The actual received signal strength is attenuated by two sources: the path loss $P_d$ is a function of the distance between the vehicle and the cell tower $d_{v-t}$ and path loss exponent $\gamma$, while
+interference, multipath effects, and other RF noise are wrapped up into a uniformly distributed random penalty $P_{int}$.
+
+The dynamics of the tower handoff, $P_{handoff}$, are modelled using two parameters.
+$P_{hyst}$ represents hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers.
+$P_{load}$ represents the load balancing efforts to distribute usage across the cell network, adding an eRSS penalty to heavily loaded towers proportional to $N_t$, the number of other vehicles already connected to tower $t$.
+
+The eRSS can then be calculated as a function of the parameter vector $\phi = \{$interference, hysteresis, load balancing$\} = \{\alpha/\gamma, \beta/\gamma, \xi/\gamma\}$ over which we conduct our sensitivity analysis, evaluating the relative impacts of handoff dynamics in the presence of RF noise on route flow estimation.
+
 \begin{eqnarray}
@@
 
-In this equation, the actual received signal strength is attenuated by two sources: the path loss $P_d$ 
-is a function of the distance between the vehicle and the cell tower $d_{v-t}$ and path loss exponent $\gamma$, while 
-interference, multipath effects, and other RF noise are wrapped up into a uniformly distributed random penalty $P_{int}$.
-
-The dynamics of the tower handoff, $P_{handoff}$, are modelled using two parameters.
-$P_{hyst}$ represents an amount of hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers.
-$P_{load}$ represents the load balancing efforts to distribute usage across the cell network, adding an eRSS penalty to heavily loaded towers.
-
-where $N_t$ is the number of other vehicles already connected to tower $t$.
-The four parameters $\{\gamma, \alpha, \beta, \xi\}$ can be scaled by the first to get our final parameter vector $\phi = \{a, b, c\} = \{\alpha/\gamma, \beta/\gamma, \xi/\gamma\}$ over which we conduct our sensitivity analysis, evaluating the relative impacts of hysteresis and load balancing in the presence of RF noise on route flow estimation.
-
 \subsection{Limitations}

### 2015-02-02 paper/intro.tex
citations + fixed figure

@@
 \section{Introduction}
-Route flow estimation on road networks is a critical problem for mobility CPS, as real-time prediction and control applications require the state of the road network.
+Route flow estimation on road networks is a critical problem for mobility CPS, as real-time prediction and control applications require the state of the road network \cite{Faouzi2011,Mathew2014}.
 Previous work has demonstrated the promise of computing an estimate from area-based sensors such as cellular towers, using a projected first-order method that scales well to large city-scale networks \cite{Wu2015}.
@@
 voronoi tessellations of cell tower regions) \cite{Voronoi1908}.
-The real world is seldom so kind.
+The real world is seldom so kind \cite{Caceres2013}.
 

### 2015-02-02 paper/experiments.tex
More revisions

--- 2015-02-02 paper/experiments.tex
@@
 \subsection{Experimental setup}
+\begin{comment}
 \begin{figure}[h!]
@@
 \end{figure}
+\end{comment}
 
-We consider a medium sized network based off of the I-210 highway corridor in Los Angeles (see Figure \ref{fig:small-network}) in the following scenarios
+We consider a medium sized network based off of the I-210 highway corridor in Los Angeles, CA in the following scenarios, where $N$ indicates the number of uniformly sampled cellular tower positions. 
 \begin{itemize}
-\item \textit{Urban sprawl} ($N=300$): We emulate a city network where the density of cell towers is sufficient for recovering route flow in the noiseless setting.
-\item \textit{City Center} ($N=375$): We emulate a popular commercial district with a dense sampling of cellular towers.
+\item \textit{Urban Sprawl (US)} ($N=300$): We emulate a city network where the density of cell towers is sufficient for recovering route flow in the noiseless setting.
+\item \textit{City Center (CC)} ($N=375$): We emulate a popular commercial district with a very dense sampling.
 \end{itemize}
+In each of the scenarios, we first compute a feasible route flow $x$ for the user equilibrium solution of the network.
+Treating $x$ as our sampling distribution, we issue 10,000 vehicles and collect the cellpath flow following the noise model described in Sec.~\ref{sec:handoff-model} across a range of parameter values $\phi$.
+%We fix the parameters $a\in\set{0,0.05,0.1}, b=\set{0, 0.05, 0.1, 0.2, 0.3},c=\set{0, .0004, .0008, .0012, .002}$. 
+For each configuration, we use the projected first-order method solver in \cite{Wu2015} to compute $\hat x$.
+We evaluate on the metric $\norm{x-\hat x}_1/\norm{x}_1$, which corresponds to the percent route flow error.
 
-\subsection{Results}
+\subsection{Preliminary results}
 
-“sparser”: smallest number of cell towers for which route flow accuracy is pretty good ($<5\%$ error); hopefully somewhat robust to handoff model
+We present preliminary numerical results on the US experiment in Fig.~\ref{fig:results1} (more detailed slices as well as results from the CC experiment have been omitted due to space limitations).
+In both experiments, there is a strong positive correlation ($R=0.78$ and $R=0.74$, respectively) between the load balancing gain and flow error, caused by unknown cell paths due to reassigned cell towers.
+Similarly, there is a positive correlation between hysteresis and flow error as switching delays cause vehicles to skip cell tower regions along their trajectories.
+This is more prominent in the denser CC experiment; in the US experiment, though, increasing hysteresis induces a dip in the flow error in the presence of other types of noise.
+This dip is caused by limiting jumps between towers near the borders of Voronoi regions.
 
-“city center”: super dense number of cell towers; handoff model should cause tons of problems here quickly
+\begin{figure}[ht]
+  \centering
+    \includegraphics[width=0.47\textwidth]{figures/results_300_hysteresis.png}
+  \caption{\footnotesize{This plot show the initial findings for $N=300$.
+In general, the percent route flow error increases as the interference increases.
+The percent route flow error first increase then decreases as the hysteresis margin is increased.
+The load balancing parameter indicates positive correlation with percent route flow error.}}
+  \label{fig:results1}
+\end{figure}

### 2015-02-02 paper/conclusion.tex
conclusion

--- 2015-02-02 paper/conclusion.tex
@@
 \section{Conclusion}
-The conclusion goes here.
+Through our investigation of a cell tower handoff noise model, it is clear that handoff dynamics and cellular tower density heavily influence the cellpaths measured (introducing unknown cellpaths due to reassigned cell towers) and the subsequent route flow estimate.
+Our results indicate that the state estimation method would benefit from an integrated model of handoff dynamics, tailored to the network at hand.
+Additionally, we observe that handoff dynamics have a magnified effect in denser networks, meaning that state estimation will likely less accurate.
+Finally, we conclude that the existing solver, which enforces a single cellpath per route, is too restrictive for the cellpaths introduced by cell tower reassignment.
+Relaxing this assumption will likely ameliorate the aforementioned effects.
+Lastly, we plan to perform a full-scale run of the route flow estimation on cellular signaling data from AT\&T in the greater Los Angeles area.

### 2015-02-02 paper/conclusion.tex
minor edits

@@
 \section{Conclusion}
-Through our investigation of a cell tower handoff noise model, it is clear that handoff dynamics and cellular tower density heavily influence the cellpaths measured (introducing unknown cellpaths due to reassigned cell towers) and the subsequent route flow estimate.
+Through our investigation of a cell tower handoff noise model, it is clear that handoff dynamics and cellular tower density heavily influence the measured cellpaths and subsequent route flow estimate.
 Our results indicate that the state estimation method would benefit from an integrated model of handoff dynamics, tailored to the network at hand.
-Additionally, we observe that handoff dynamics have a magnified effect in denser networks, meaning that state estimation will likely less accurate.
+Additionally, we observe that handoff dynamics have a magnified effect in denser networks, meaning that state estimation will likely be less accurate.
 Finally, we conclude that the existing solver, which enforces a single cellpath per route, is too restrictive for the cellpaths introduced by cell tower reassignment.

### 2015-02-02 paper/experiments.tex
minor edits

@@
 We present preliminary numerical results on the US experiment in Fig.~\ref{fig:results1} (more detailed slices as well as results from the CC experiment have been omitted due to space limitations).
-In both experiments, there is a strong positive correlation ($R=0.78$ and $R=0.74$, respectively) between the load balancing gain and flow error, caused by unknown cell paths due to reassigned cell towers.
+In both experiments, there is a strong positive correlation ($R=0.78$ and $R=0.74$, respectively) between the load balancing gain and flow error, caused by unknown cellpaths due to reassigned cell towers.
 Similarly, there is a positive correlation between hysteresis and flow error as switching delays cause vehicles to skip cell tower regions along their trajectories.
